---
title: "Correlation Report"
output: html_document
---


```{r, set-chunk-opts, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```
## Introduction

This report examines the correlation between lecture video length and engagement in class. Engagement will be measured by the number of views on each video. 

## Reading the Data

```{r, load-data}
here::i_am("subanalysis_Stephens/report/correlation_report.Rmd")
data <- readRDS(
  file = here::here("data/data.rds")
)
```


## Correlation Analysis

Below we report a scatter plot of views as a function of 
video lecture length. 

```{r, plot-data}
#| fig.align = "center",
#| out.width = "800px"
readRDS(
  here::here("subanalysis_Stephens/output/scatter.rds")
)
```
```{r, pearson}
readRDS(
  file = here::here("subanalysis_Stephens/output/pearson.rds")
)
```

## Conclusion

Since the p-value is less than 0.05, we can conclude that there is no association between length of lecture video and the class engagement measured by views. 